Parameterized convection, stratiform clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-23 resolution.tex
edits

\begin{figure}
\begin{center}
\noindent\includegraphics[width=14pc,angle=0]{figs/temp_4zonal.pdf}\\
\end{center}
\caption{Zonal mean (a) R-values and (b) sensitivity parameter in the logistic regression, (c) climatological surface latent heat fluxes and (d) drizzle fraction.}
\label{fig:4zonal}
\end{figure}

@@

>>>>

\begin{figure}
\begin{center}
\noindent\includegraphics[width=14pc,angle=0]{figs/temp_4zonal.pdf}\\
\end{center}
\caption{Zonal mean (a) R-values and (b) sensitivity parameter in the logistic regression, (c) climatological $\langle f_{d} \rangle \langle \omega_{d} \rangle$ and (d) climatological $FREQZM$.}
\label{fig:4zonal}
\end{figure}

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=14pc,angle=0]{figs/temp_2zonal.pdf}\\
\end{center}
\caption{Climatological, zonal mean (a) drizzle fraction and (b) surface latent heat fluxes in the convergence experiment. Drizzle fraction refers to the fractional contribution of $\leq 5$ mm/day convective precipitation rates to all convection precipitation rates, for the duration of the simulations and computed from 6-hourly instantaneous fields.}
\label{fig:2zonal}
\end{figure}
